### 2020-07-10 nb/analysis_in_R.Rmd
function works but points totals aren't right for some reason

    return(list(league_table, home_score, away_score))
}
```

@@

```{r}
for m in unique(league$matchId){

    match <- league[league$matchId==m,]
    home_team <- unique(match[match$home_or_away=='Home']$team)
    away_team <- unique(match[match$home_or_away=='Away']$team)
    home_goals <- nrow(match[match$to_team=='Home Goal',])
    away_goals <- nrow(match[match$to_team=='Away Goal',])

@@

    league_table[]

        league_table[team]
    }

@@

>>>>

    for (m in unique(league$matchId)){

        match <- league[league$matchId==m,]
        home_team <- unique(match[match$home_or_away=='Home',]$team)
        away_team <- unique(match[match$home_or_away=='Away',]$team)
        home_goals <- nrow(match[match$to_team=='Home Goal',])
        away_goals <- nrow(match[match$to_team=='Away Goal',])

        if (home_goals > away_goals){
            league_table[home_team,'W'] <- league_table[home_team,'W'] + 1
            league_table[away_team,'L'] <- league_table[away_team,'L'] + 1
        } else if (away_goals > home_goals){
            league_table[home_team,'L'] <- league_table[home_team,'L'] + 1
            league_table[away_team,'W'] <- league_table[away_team,'W'] + 1    
        } else if (home_goals == away_goals) {
            league_table[home_team,'D'] <- league_table[home_team,'D'] + 1
            league_table[away_team,'D'] <- league_table[away_team,'D'] + 1
        }

        league_table[home_team,'GF'] <- league_table[home_team,'GF'] + home_goals
        league_table[away_team,'GF'] <- league_table[away_team,'GF'] + away_goals
        league_table[home_team,'GA'] <- league_table[home_team,'GA'] + away_goals
        league_table[away_team,'GA'] <- league_table[away_team,'GA'] + home_goals

        for (team in c(home_team, away_team)){
            league_table[team,'GD'] <- league_table[team,'GF'] - league_table[team,'GA']
            league_table[team,'PTS'] <- 3*league_table[team,'W'] + 1*league_table[team,'D']
        }

    }
    return(list(league_table, home_score, away_score))
}
```

```{r}
results <- LeagueResults(events)
```

```{r}
league_table <- data.frame(results[[1]])
```

```{r}
league_table[order(-league_table$PTS),]
```

```{r}
results[[2]]
```

```{r}
results[[3]]
```

```{r}
[order(league_table[,1])]
```

```{r}
table
```

@@

```{r}
for (m in unique(league$matchId)){

    match <- league[league$matchId==m,]
    home_team <- unique(match[match$home_or_away=='Home',]$team)
    away_team <- unique(match[match$home_or_away=='Away',]$team)
    home_goals <- nrow(match[match$to_team=='Home Goal',])
    away_goals <- nrow(match[match$to_team=='Away Goal',])

@@

    if (home_goals > away_goals){
        league_table[home_team,'W'] <- league_table[home_team,'W'] + 1
        league_table[away_team,'L'] <- league_table[away_team,'L'] + 1
    } else if (away_goals > home_goals){
        league_table[home_team,'L'] <- league_table[home_team,'L'] + 1
        league_table[away_team,'W'] <- league_table[away_team,'W'] + 1    
    } else if (home_goals == away_goals) {
        league_table[home_team,'D'] <- league_table[home_team,'D'] + 1
        league_table[away_team,'D'] <- league_table[away_team,'D'] + 1
    }

    league_table[home_team,'GF'] <- league_table[home_team,'GF'] + home_goals
    league_table[away_team,'GF'] <- league_table[away_team,'GF'] + away_goals
    league_table[home_team,'GA'] <- league_table[home_team,'GA'] + away_goals
    league_table[away_team,'GA'] <- league_table[away_team,'GA'] + home_goals

    for (team in c(home_team, away_team)){
        league_table[team,'GD'] <- league_table[team,'GF'] - league_table[team,'GA']
        league_table[team,'PTS'] <- 3*league_table[team,'W'] + 1*league_table[team,'D']
    }

@@

```{r}
league_table['Arsenal',]
```
